### 2014-06-28 Choosing R3 Relations.tex
trying_additional_triangle_relation

\begin{lem}
The two relations $s_{1}^{-1}s_2^{-1}s_3^{-1}s_2s_1s_2^{-1}s_3s_2 = e$ and $\twi\tri\oni\tr\twi\tri\on\tr =e$ are equivalent and they imply $\tr\on\tw\on\tri\oni\tw\oni\tri\oni\twi\on=e. $
\end{lem}
\begin{proof}

@@

Next,I claim $\tw\tr = \oni\tr\on\tr\on\tw\tri\oni.$ NOTE: I FIGURED OUT HOW TO DO THIS BEFORE, BUT IM TOO TIRED NOW, AND I COULD HAVE MADE A MISTAKE, SO SOMEONE ELSE SHOULD CHECK, IF ITS WRONG THIS IS ALL WRONG.
This should be easy to verify by manipulating the equation $\twi\tri\oni\tr\twi\tri\on\tr =e.$ Plugging this in yields
\begin{align*}
	e &= (\oni\tr\on\tr\on\tw\tri\oni)(\on\tr\on\tri\oni\tw\oni\on\tri\oni)(\on\tr\oni\tri\oni\twi\on\oni\tri\on)
	\\
	&= (\oni\tr\on\tr\on\tw\on\oni\tri\oni)(\on\tr\on\tri\oni\tw\oni\on\tri\oni)(\on\tr\oni\tri\oni\twi\on\oni\tri\on)
	\\
	&= (\oni\tr\on\tr\on\tw\on)(\tri\oni\tw\oni\on\tri\oni)(\on\tr\oni\tri\oni\twi\on\oni\tri\on)
	\\
	&= (\oni\tr\on\tr\on\tw\on)(\tri\oni\tw\oni)(\tri\oni\twi\on\oni\tri\on)
	\\
	&= (\oni\tr\on\tr\on\tw\on)(\tri\oni\tw\oni)(\tri\oni\twi\on\oni\tri\on)
\end{align*}

>>>>

\begin{rem}
I am proposing to add the additonal $s_as_as_b = s_bs_as_a$ whenever there is a 2 edge pointing to $a$, a 1 edge pointing from $a$ to $b$, and a 2 edge pointing out of $b.$ I'm not sure whether this helps the rest of the problem, but it allows us to deduce the analog for $R3(b).$ We can also note that this relation would definitely not show up in the coexeter groups because $s_a^2 = e.$
\end{rem}

\begin{lem}
Assuming the additional relation $\tw\tr\tr = \tr\tr\tw.$ The two relations $s_{1}^{-1}s_2^{-1}s_3^{-1}s_2s_1s_2^{-1}s_3s_2 = e$ and $\twi\tri\oni\tr\tw\tri\on\tr =e$ are equivalent and they imply $\tr\on\tw\on\tri\oni\tw\oni\tri\oni\twi\on=e. $
\end{lem}
\begin{proof}

@@

Next,I claim $\tw\tr = \oni\tr\on\tr\on\tw\tri\oni.$ This should be easy to verify by manipulating the equation $\twi\tri\oni\tr\tw\tri\on\tr =e,$ if we can use the relation $\tw\tr\tr = \tr\tr\tw,$ we can obtain $\tw\tr = \oni\tr\on\tr\on\tw\tri\oni.$

 Plugging this in yields
\begin{align*}
	e &= (\oni\tr\on\tr\on\tw\tri\oni)(\on\tr\on\tri\oni\tw\oni\on\tri\oni)(\on\tr\oni\tri\oni\twi\on\oni\tri\on)
	\\
	&= (\oni\tr\on\tr\on\tw\on\oni\tri\oni)(\on\tr\on\tri\oni\tw\oni\on\tri\oni)(\on\tr\oni\tri\oni\twi\on\oni\tri\on)
	\\
	&= (\oni\tr\on\tr\on\tw\on)(\tri\oni\tw\oni\on\tri\oni)(\on\tr\oni\tri\oni\twi\on\oni\tri\on)
	\\
	&= (\oni\tr\on\tr\on\tw\on)(\tri\oni\tw\oni)(\tri\oni\twi\on\oni\tri\on)
	\\
	&= (\oni\tr\on\tr\on\tw\on)(\tri\oni\tw\oni)(\tri\oni\twi\on\oni\tri\on)
\end{align*}
